Researchers preferentially collaborate with same-gendered colleagues across

### 2018-10-24 manuscript/Response_letter.Rmd

**As suggested, we now calculate $\alpha$ for every suitable PubMed paper in our dataset (3.7 paper, 16m authors), ignoring the journal and publication date, to see if it inflates $\alpha$ as we expected. Reassuringly, the $\alpha$ for PubMed as a whole is 0.126, which is almost double the median $\alpha$ calculated on 1-year datasets for individuals journals (i.e. our main result, shown in Figure 1), supporting our theoretical argument that ignoring the Wahlund effect does add a non-trivial amount of inflation to $\alpha$.**

  - Line 246 "our results provide non-experimental support for the hypothesis that mixed-gender teams produce better research than single-gender teams" is better said this way than in the abstract

**We feel that both phrasings are carefully chosen, and accurately reflect what we found in the study. For comparison, the Abstract equivalent of this sentence reads, "Interestingly, journals with a high impact factor for their discipline tended to have comparatively low homophily, as predicted if mixed-gender teams produce better research." Note that: 1) the word 'Interestingly' reflects our feeling that this result is an unexpected curio that requires follow up study (although there are already some experimental studies examining the effects of diversity on the success of team-based projects, which we cite), 2) the word 'tended' stresses that this is not a hard-and-fast finding, but rather a noisy correlation, and 3) the word 'predicted' stresses to the reader that this result is consistent with the theory but does not prove it (that is, we do not commit the fallacy of 'affirming the consequent').**

- line 257: "Given that many collaborative research projects unfortunately involve a gendered division of labour [61], working with a same-gendered colleague may provide exposure to new parts of the research process, and (especially for the minority gender) a welcome change of pace." Not sure I understand (/agree with) the logic behind this last sentence. Do you mean that if you collaborate with a same-gendered colleague, you may end up doing things that are different than if you collaborated with a different-gendered colleague? This sounds a bit odd to me... A different type of interaction, different level of implication, sure. But if I am a lab tech, working with a male or female PI won't really make me change the type of work that I do -- or will it?
And I am not sure I understand what is alluded to by "welcome change of pace"...

**You mention the right answer here -- our intended meaning was "a different type of interaction". For women working in a field where women are the minority (e.g. mathematics or surgery), the majority of their professional interactions will be with men, and so working with another woman would be a (perhaps welcome) novelty, given that men and women differ consistently in various traits (and that some people sometimes respond differently to male-female collaborator pairs relative to same-sex pairs, e.g. by making gender-based assumptions about who did what towards the project).**

#### Supplementary
- Kudos for providing the code! Rmarkdown is wonderful (show/hide comments is also a great feature!).

**Thanks, we agree it's an excellent tool for presenting the details of a coding-intensive analysis and maximising its transparency, reproducibility, and potential to be adapted and re-used by other researchers.**

- Could there be a pdf output as well? and a table of contents and lists of tables/figures? To avoid having to use ctrl-F to find the supplementary figures...

**If the MS is accepted, PLOS will ask us to upload all the supplementary figures and tables one by one, giving a clickable route to each one of the supplementary figures in the paper itself, and so it's not necessary to make a table of contents for our HTML supplement. As for making it into a PDF, this doesn't seem useful (since it will contain the same information, but will lose all the nice features of HTML), but we're happy to do it if asked to by the copy editors. This will simply involve opening the HTML document using a web browser, then saving it as a PDF; we can do this if asked, or leave it up to any readers who need a PDF copy (note that HTML can be opened using any web browser, and is likely to be just as future-proof as PDF).**

- Fig S2 seems to be missing.

**Thanks, we fixed a typo and the figure now shows up.**
